Review of Edge Detectors

### 2014-05-09 review/review_answer_2.tex

\subsection{ Minor comments}
\subsubsection{ In gaussian\_kernel}
The normalization by the sum is different from the one evoked in Section
4.1.1. You should either change the implementation or comment on this in the article. Note
also that the comment in the code correspond to the formula in the pdf instead of the implemented one.

\subsubsection{ In LoG\_kernel }
The same problem of consistency for the normalization occurs here. It is in
fact worse than in the gaussian case, since I suppose that the LOG kernel does not sum to one. Besides dividing by $sigma^4$ is pointless if you normalize by the sum! Of course, kernel normalization has no impact on the edge detection since the thresholds are expressed in a relative way.

\subsubsection{ In the README:}
\que you announce that:
"More than one algorithm can be applied to the same image with the same
command. For example:
edges -r 0.1 -l 3 29 0.13 molino.png
will apply Roberts' algorithm with threshold parameter 0.1, and the
Marr-Hildreth (LoG) with parameters sigma=3.00, N=29, TZC=0.13;"
You should also warn that each algorithm can be launched only once. For instance
the following call will fail:
edges -r 0.1 -r 0.2 -l 3 29 0.13 molino.png

\section{ Conclusion}
Overall I think the submission is a good candidate for IPOL but it cannot be
accepted in the current state. My main complain relates to the poor quality of
the PDF:
\begin{verbatim}
- many explanations are unstructured
- the writing is often bad (I am under the impression that the pdf was submitted without
proofreading)
- Except for the algorithmic description that is sufficiently detailed, many
aspects are lacking: specifically in the experimental part and the conclusion.
\end{verbatim}
